---
title: "test plots"
author: "Emily"
date: "16/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestplot)
library(broom)
#Libraries
library(dplyr)
#library(tidyft) - only call tidyft if/when needed as it masks lots of other functions
library(plyr)
library(tidyverse)
library(survival)
library(ggplot2)
library(tidyselect)
library(tidyr)
```

```{r function, echo=FALSE}
plot_HRs <- function(model, title = "" , cex=1){
 # model <- z.fit.F.D
#  cex <-1
#  title = "testing"
  
  STAT <- as.data.frame(summary(model)$coef)
  STAT <- STAT[!grepl("pspline", rownames(STAT)),]
  CI <- as.data.frame(summary(model)$conf.int)
  CI <- CI[!grepl("ps\\(", rownames(CI)),]  
  #"term"      "estimate"  "std.error" "statistic" "p.value"   "conf.low"  "conf.high"
  term <- rownames(STAT)
  estimate <- as.numeric(CI[,1])
  conf.low <- as.numeric(CI[,3])
  conf.high<- as.numeric(CI[,4])
  std.error <- as.numeric(STAT[,2])
  statistic <- as.numeric(STAT[,4])
  p.value <-as.numeric(STAT[,6])
  mod.df <- as.data.frame(cbind(term, estimate,std.error ,statistic, p.value ,conf.low, conf.high))
  
 # length(estimate)
  vars <- c(  "estimate",  "std.error" ,"statistic", "p.value" ,  "conf.low" , "conf.high")
  mod.df <-mod.df %>% mutate_at(vars, as.character) %>% mutate_at(vars, as.numeric)
  mod.df$term <- as.character(mod.df$term)
  
  df1 <- mod.df %>% 
    transmute( 
      HR = estimate, 
      low = conf.low, 
      high = conf.high
    )
 
  ci <- paste0(  "(" ,formatC(as.numeric(conf.low), format = 'f', flag='0', digits = 2)  , # formatC keeps trailing 0
                 " - ", formatC(as.numeric(conf.high), format = 'f', flag='0', digits = 2)  , ")")
  HR_w_ci <- paste0( formatC(as.numeric(df1$HR), format = 'f', flag='0', digits = 2), " ", ci)
  
  row_names <- cbind(c("Name", mod.df$term),
                     c("Adjusted hazard ratio (95% CI)",HR_w_ci))
  df1 <- rbind(rep(NA, 4), df1)
  
  
  forestplot(labeltext = row_names , #[c(1:6, 35:42),],
             df1[, c("HR", "low", "high")],
             is.summary=c(FALSE, FALSE, FALSE),
             zero      = 1,
              clip=c(0.01,64), 
             xlog      = TRUE, 
             boxsize = .3,
             txt_gp = fpTxtGp(label = gpar(fontfamily = "", cex= cex), 
                              ticks = gpar(fontfamily = "", cex = cex)), 
             title = title)
  
  }



splineplot <- function(df=ptemp, term, centre, title = "" ){
 # df <- ptemp
#  term <- "Age"
#  centre <- 20
  timeterm <- df[[term]]
  center <- with(timeterm, y[x== centre])
  ytemp <- timeterm$y + outer(timeterm$se, c(0, -1.96, 1.96),'*')
  matplot(timeterm$x, exp(ytemp - center), log='y',type='l', lty=c(1,2,2), col=1,
          xlab= term, ylab="Relative hospitalisation rate", 
          main = title)
  abline(h=1, lty=2)
}
```

##Modelling the second wave

Risk models were fitted for hospitalisation and death for the second wave (1st July onwards). Males and females were modelled separately. All aalible qcovid risk groups were fitted. Age, BMI and townsend score were fitted as splines. 

## Risk models for Death
```{r data death , echo =FALSE}

z.fit.M.D <- readRDS("/conf/EAVE/GPanalysis/QCovid_Validation/output/EM_Model_Death_Male2W.rds")
z.fit.F.D <- readRDS("/conf/EAVE/GPanalysis/QCovid_Validation/output/EM_Model_Death_Female2W.rds")
z.fit.M.H <- readRDS("/conf/EAVE/GPanalysis/QCovid_Validation/output/EM_Model_Hosp_Male2W.rds")
z.fit.F.H <- readRDS("/conf/EAVE/GPanalysis/QCovid_Validation/output/EM_Model_Hosp_Female2W.rds")
```
Description of modelling....


#### Females, deaths
```{r splineplots FD, echo=FALSE}
ptemp <- readRDS( "/conf/EAVE/GPanalysis/QCovid_Validation/output/temp/ptemp_F_D2W.rds")

midtown <- (ptemp$town$x)[round(length(ptemp$town$x)/2)]
splineplot(ptemp, "town", centre = midtown , title = "Females death risk by -  Townsend score")

splineplot(ptemp, "BMI", centre = 22 , title = "Females death risk by -  BMI")

splineplot(ptemp, "Age", centre = 20 , title = "Females death risk by -  Age")

rm(ptemp)
```

```{r Females death, fig.width=16, fig.height=24, echo=FALSE}  
 
plot_HRs(z.fit.F.D, title = "Females - Death. Adjusted for age, BMI and townsend score", cex=1.5)
```

#### males deaths
```{r splineplots MD, echo=FALSE}
ptemp <- readRDS( "/conf/EAVE/GPanalysis/QCovid_Validation/output/temp/ptemp_M_D2W.rds")


midtown <- (ptemp$town$x)[round(length(ptemp$town$x)/2)]

splineplot(ptemp, "town", centre = midtown , title = "Males death risk by -  Townsend score")

splineplot(ptemp, "BMI", centre = 22 , title = "Males death risk by -  BMI")

splineplot(ptemp, "Age", centre = 20 , title = "Males death risk by -  Age")

rm(ptemp)
```


```{r males death, fig.width=16, fig.height=24 , echo=FALSE}  
 
plot_HRs(z.fit.M.D, title = "Males - Death. Adjusted for age, BMI and townsend score", cex=1.5)
```


### Females hospitalisation
```{r splineplots FH, echo=FALSE}
ptemp <- readRDS( "/conf/EAVE/GPanalysis/QCovid_Validation/output/temp/ptemp_F_H2W.rds")

midtown <- (ptemp$town$x)[round(length(ptemp$town$x)/2)]
splineplot(ptemp, "town", centre = midtown, title = "Females hospitalisation risk by -  Townsend score")

splineplot(ptemp, "BMI", centre = 22 , title = "Females hospitalisation risk by -  BMI")

splineplot(ptemp, "Age", centre = 21 , title = "Females hospitalisation risk by -  Age")

rm(ptemp)
```

```{r Females hosp, fig.width=16, fig.height=24, echo=FALSE}  
 
plot_HRs(z.fit.F.H, title = "Females - hospitalisation. Adjusted for age, BMI and townsend score", cex=1.5)
```

#### Males hospitalisation

```{r splineplots MH, echo=FALSE}
ptemp <- readRDS( "/conf/EAVE/GPanalysis/QCovid_Validation/output/temp/ptemp_M_H2W.rds")

midtown <- (ptemp$town$x)[round(length(ptemp$town$x)/2)]

splineplot(ptemp, "town", centre = midtown, title = "Males hospitalisation risk by -  Townsend score")

splineplot(ptemp, "BMI", centre = 22 , title = "Males hospitalisation risk by -  BMI")

splineplot(ptemp, "Age", centre = 23 , title = "Males hospitalisation risk by -  Age")

rm(ptemp)
```


```{r males hosp, fig.width=16, fig.height=24, echo=FALSE}  
 
plot_HRs(z.fit.M.H, title = "Males - hospitalisation.  Adjusted for age, BMI and townsend score", cex=1.5)
```
